The Aho-Corasick algorithm is a cornerstone of signature-based network
intrusion detection systems and malware analysis tools, because of its linear-time
complexity in the size of the input. Its state-transition dependency, however,
ties the canonical implementation to sequential execution, leaving modern
multi-core processors underused. This work designs, implements, and evaluates
data-parallel scanning strategies built on POSIX Threads for shared-memory
multi-core CPUs. The input text is partitioned into overlapping segments that
worker threads scan concurrently over a shared, strictly read-only automaton,
keeping the hot path free of locks; a flattened, contiguous output layout is
also proposed to eliminate the pointer-chasing cost of emitting matches. The
study deliberately targets the memory-bound regime where the automaton greatly
exceeds the last-level cache, using realistic Snort and Emerging Threats rule
sets (up to roughly $507$~MiB of automaton) over multi-gigabyte corpora on a
hybrid Intel Core i5-1235U processor. The results show that text-level data
parallelism outperforms pattern-set partitioning: search speedups reach up
to $4.79\times$ on the canonical corpus and $4.52\times$ on the multi-gigabyte
corpus --- both at twelve threads for the same moderate dictionary --- while the
flattened layout adds a regime-dependent gain
that grows with memory pressure, up to $+13.0\%$ on a single thread. When the
automaton is forty-two times larger than the cache, however, throughput drops by
$74.0\%$ and parallel scaling collapses: on the canonical corpus the speedup
peaks near $2.85\times$ at six threads and then regresses, while on the
multi-gigabyte corpus it saturates at only $2.79\times$ at twelve threads,
exposing memory bandwidth as the physical ceiling. Whole-pipeline (build,
search, and merge) accelerations reach $4.50\times$ on the moderate dictionary
and $2.76\times$ on the memory-bound one; since construction is under one percent
of the runtime, these track the search-only speedups almost exactly. The central finding is that, once the automaton exceeds the
last-level cache, the dominant barrier to scaling Aho-Corasick is
microarchitectural --- namely cache overflow and DRAM bandwidth --- rather than
the matching logic itself.
