This appendix documents the protocol used to query the raw measurement
database from which every result reported in this thesis is derived, including
the end-to-end wall-clock times of Table~\ref{tab:e2e}. Those end-to-end figures
are not a separate campaign: each is the sum of two quantities that the canonical
sweep already records for the corresponding execution---the construction time
(\texttt{build\_ms}) and a single full-corpus search pass (\texttt{mean\_ms}).
They can therefore be reproduced and audited from the same database as every
other figure.
The benchmark campaign stores its measurements in a single typed SQLite
database located at \texttt{parallel-aho-corasick/runs/i5/sweep.db},
containing one \texttt{runs} table (one row per timed execution) and a
set of aggregating views. The headline figures are retrieved from these views
instead of the raw execution logs.

\subsecao{Artifact Availability}

The complete artifacts of this work are publicly available in two Git
repositories: the \LaTeX{} source of this document at
\url{https://github.com/MTheus22/acceleration-of-pattern-matching-algorithms-using-parallel-programming},
and the C implementation---together with the searchers, the benchmark harness,
the dataset descriptors, and the measurement database---at
\url{https://github.com/MTheus22/parallel-aho-corasick}. Every empirical figure
reported in this thesis is derived from the latter repository. After cloning it,
the sequential and parallel searchers can be built and exercised through the
project Makefile: \texttt{make} compiles the laboratory, \texttt{make test}
checks that every strategy reproduces the exact match set of the sequential
baseline, \texttt{make digest} runs the MD5 multiset validation described in
Section~\ref{subsec:correctness} (up to sixty-four threads), and
\texttt{make bench} executes the measurement sweep. The remainder of this
appendix documents the schema and the canonical queries of the resulting
measurement database, so that each headline number can be traced back to the
raw measurements.

\subsecao{Database Schema}

Each row of the \texttt{runs} table identifies an execution by its phase,
pattern dictionary, corpus, searcher strategy, and thread count. It records the
timing statistics (minimum, mean, median, and maximum wall-clock time in
milliseconds, along with the coefficient of variation across the timed
iterations), the derived throughput (in MB/s and Gbit/s), the input volume and
match count, and the automaton descriptors (pattern count, number of states,
footprint in kibibytes, and sequential or parallel build time). The views
listed in Table~\ref{tab:dbviews} pre-aggregate the data so no headline
figure requires ad hoc post-processing of the raw rows.

\begin{table}[H]
    \centering
    \caption{Aggregating views of the measurement database.}
    \label{tab:dbviews}
    \small
    \begin{tabular}{@{} l p{8.8cm} @{}}
        \toprule
        \textbf{View} & \textbf{Question it answers} \\
        \midrule
        \texttt{v\_speedup}       & Speedup of each searcher against the single-threaded sequential baseline. \\ \addlinespace
        \texttt{v\_self\_speedup} & Self-relative scalability: throughput at $T$ threads over throughput at one thread. \\ \addlinespace
        \texttt{v\_footprint}     & Throughput as a function of the automaton footprint, at one and twelve threads. \\ \addlinespace
        \texttt{v\_build}         & Speedup of the parallel automaton construction over the sequential build. \\ \addlinespace
        \texttt{v\_best}          & Best-performing searcher for each dictionary, corpus and thread count. \\ \addlinespace
        \texttt{v\_correctness}   & Number of distinct match counts per dictionary and corpus (a value of one indicates agreement). \\
        \bottomrule
    \end{tabular}

    {\footnotesize\raggedright \textbf{Source:} Prepared by the author. \par}
\end{table}

\subsecao{Canonical Queries}

The queries below reproduce the main results of the study. They can be executed
against the database using the standard \texttt{sqlite3} client.

\begin{verbatim}
-- Speedup curve of a searcher (Snort dictionary, canonical corpus)
SELECT thr, speedup_vs_seq FROM v_speedup
WHERE patterns='patterns_snort' AND corpus='enron_corpus'
  AND searcher='pthread_dynamic' ORDER BY thr;

-- Peak speedup per scenario (winning searcher and thread count)
SELECT patterns, corpus, searcher, thr, speedup_vs_seq FROM v_speedup w
WHERE speedup_vs_seq = (SELECT MAX(speedup_vs_seq) FROM v_speedup x
  WHERE x.patterns = w.patterns AND x.corpus = w.corpus)
ORDER BY patterns, corpus;

-- Footprint versus throughput at twelve threads (cache blowout)
SELECT patterns, automaton_mib, searcher, mbps FROM v_footprint
WHERE thr = 12 ORDER BY automaton_mib;

-- Speedup of the parallel automaton construction
SELECT patterns, build_threads, build_speedup FROM v_build
ORDER BY patterns, build_threads;

-- End-to-end wall-clock (build + one full-corpus scan) on enron_x8
SELECT patterns, searcher, thr, build_ms, mean_ms,
       build_ms + mean_ms AS e2e_ms
FROM runs
WHERE corpus='enron_x8' AND thr IN (0, 12)
  AND searcher IN ('sequential','pthread_chunked_flat','pthread_chunked_v3_flat')
ORDER BY patterns, searcher, thr;
\end{verbatim}

Before any timing was reported, the correctness of every parallel strategy was
verified using the \texttt{v\_correctness} view. This view returns a single
distinct match count for each dictionary and corpus, confirming that all
strategies reproduce the exact match set of the sequential baseline.
