This thesis investigated data-parallel scanning strategies and
microarchitectural optimizations to accelerate the Aho-Corasick multi-pattern
matching algorithm on shared-memory multi-core CPUs, using the POSIX Threads
programming model. The work targeted a specific computational regime rather than
a particular machine: the behaviour of multi-pattern matching when the automaton
greatly exceeds the last-level cache, which is typical for signature-based
intrusion detection with realistic rule sets.

% review: issue #158, comment 062 --- the central thesis is stated as a
% regime-level finding, with magnitudes deferred to the per-platform sections,
% so the conclusion no longer reads as a single universal verdict drawn from one
% machine.
At the level of computational regime, three findings are supported by the
platforms tested and form the core contribution. First, once the automaton no
longer fits in the last-level cache, the dominant constraint is the memory
subsystem, not the matching logic: automaton footprint governs throughput in the
large-corpus workloads. The broader i5 sweep also indicates that corpus content
is secondary in this regime, but that cross-corpus axis was not repeated on the
workstation. Second, the axis with the most leverage is text-level partitioning
with a read-only shared automaton; partitioning the dictionary instead of the
text yields only a small, locality-driven gain that saturates early and never
approaches text parallelism. Third, a flat output layout that replaces
pointer-chasing with contiguous reads is the simplest effective optimization and
remains useful under memory pressure. Two strategies were falsified on every
platform: dictionary sharding alone never approaches text parallelism, and
combining sharding with chunking is consistently slower than flat-output text
chunking, because scanning the text once per shard multiplies the memory traffic
that is already the bottleneck. These negative results are part of the
contribution: they rule out plausible approaches and reinforce that, whenever the
working set is memory-bound, DRAM bandwidth---not the matching code---is the
binding constraint, so text parallelism combined with a cache-friendly layout is
the correct approach. What does \emph{not} generalize is the absolute magnitude
of the gains and the shape of the scaling curve: those depend on the memory
subsystem and core topology of the machine, as the two platforms below make
explicit.

\subsecao{Findings on the Reference Platform}

The complete experimental study was conducted on the Intel i5-1235U, a mobile
hybrid processor with two performance cores, eight efficiency cores, and a
12~MiB last-level cache; it remains the source of truth for the headline numbers,
tables, and figures of this thesis. Text-level partitioning with a boundary
overlap of $L_{\max}-1$ bytes scales sublinearly, reaching $4.52\times$ at twelve
threads on the multi-gigabyte corpus and a canonical-corpus peak of $4.79\times$
via dynamic dispatch. As the dictionary grows from a cache-resident set to one
forty-two times larger than the last-level cache, single-threaded throughput
falls by $74.0\%$, and the parallel speedup drops accordingly: in the
memory-bound regime the speedup peaks at $2.85\times$ near six threads on the
canonical corpus and then regresses as further threads are added. This regression
is a property of this constrained platform, not of the algorithm: the i5's narrow
memory subsystem and its two performance cores saturate before all twelve
hardware threads are used, an effect that the homogeneous workstation in the next
section does not reproduce. The corresponding parallel efficiency at
twelve threads is $37.7\%$ for the moderate-dictionary regime and $23.3\%$ for the
memory-bound one, reflecting DRAM saturation as the dominant overhead rather than
an inherent serial fraction of the algorithm.

On this heterogeneous processor, frequency-weighted partitioning and dynamic
dispatch removed the load imbalance of uniform segments, reducing the per-thread
coefficient of variation from up to $53\%$ to under $5\%$. This improves
predictability rather than peak throughput, since memory remains the bottleneck.
The proposed flat output layout reached $+13.0\%$ on a single thread exactly in
the memory-bound regime where it matters most. Parallelizing the construction of
the automaton accelerated the build of the largest dictionary by up to
$1.55\times$, a useful operational gain for rule reloading, though negligible in
the total time of a multi-gigabyte scan. End-to-end, the full pipeline achieves
$4.50\times$ on the moderate dictionary and $2.76\times$ on the memory-bound
one---figures that track the search-only speedups, since construction is under
one percent of the runtime.

The three specific objectives from the introduction were fully met on this
platform. The first---to design and implement a parallel Aho-Corasick algorithm
in C using the POSIX Threads API, exploiting intra-input parallelism on
shared-memory multi-core CPUs---was met through a family of text-partitioning,
load-balancing, and output-layout strategies whose correctness was validated
exhaustively across all tested workloads. The second---to quantify performance
gains in terms of speedup, throughput, and parallel efficiency against a
sequential baseline---was met by reporting search speedups of $4.79\times$
(canonical corpus, dynamic dispatch) and $4.52\times$ (multi-gigabyte corpus,
flat-output chunking), alongside parallel efficiencies of $37.7\%$ and $23.3\%$
for the moderate-dictionary and memory-bound regimes, respectively. The
third---to analyze scalability under different workloads, pattern sets, and thread
counts---was met through a systematic test across seven thread counts, three
corpora, and automata covering a forty-two-fold range of cache capacity, which
identified and quantified the memory bandwidth saturation point and the subsequent
performance drop.

\subsecao{Portability to a Homogeneous Many-Core CPU}

% review: issue #158, comment 062 --- the portability run is reported as
% confirmation and delimitation of the i5 study, not as a replacement source of
% truth, so the thesis no longer over-generalizes a single hybrid machine.
A portability run on a homogeneous AMD Ryzen 9 9950X (sixteen identical cores,
thirty-two hardware threads, a 64~MiB last-level cache split across two core
complexes), executed on the same corpora and dictionaries, separates the general
findings above from the artifacts of the hybrid mobile chip. It confirms the
core thesis. The cache cliff persists: single-threaded throughput still falls
by about $67\%$ from the smallest to the largest automaton, so the memory-bound
regime is structural rather than an artifact of the i5's small cache. The
strategy hierarchy is unchanged---text partitioning beats pattern sharding, the
flat layout beats the chained one, and parallel construction tops out at
$1.57\times$, essentially the $1.55\times$ algorithmic ceiling measured on the i5
despite eight times as many cores.

At the same time, the workstation shows that several phenomena reported for the
i5 are specific to constrained or heterogeneous hardware, not universal laws.
Where the i5 regresses past six threads, the Ryzen scales monotonically to
$22.72\times$ on the moderate dictionary and $19.79\times$ on the memory-bound one
at thirty-two threads, sustaining about $89\%$ parallel efficiency at sixteen
threads. The low i5 efficiency therefore reflects a narrow memory subsystem
compounded by performance/efficiency-core asymmetry, not a large serial fraction
intrinsic to the algorithm. The elaborate topology-aware load balancing that was
central on the i5 becomes unnecessary on identical cores, where simple static
distribution already drives the per-thread coefficient of variation to about
$0.1\%$; and the finding that no single strategy dominates across regimes is an
i5 effect---on the uniform machine a single flat dynamic variant wins in both
regimes. A larger machine with uniform cores and more memory channels thus delays
the bottleneck and scales much further, but it does not eliminate the bottleneck:
the memory-bound regime survives the change of hardware.

\subsecao{Threats to Validity}

The principal study rests on a single mobile, hybrid processor with a limited
sustained-load envelope, which made long tests sensitive to scheduler, affinity,
and operating-condition variance; the reported numbers are conservative
under-load values, and the variability is documented rather than hidden. The
Ryzen 9 9950X run reduces, but does not eliminate, the external-validity threat:
it confirms the memory-bound thesis on a second microarchitecture, yet both
machines share a single-socket, single-NUMA-node design, and neither was
instrumented with hardware performance counters. The microarchitectural
explanations are therefore consistent with the timing data but were not confirmed
by direct telemetry of cache misses, memory bandwidth, or pipeline stalls. A
controlled re-run of the i5 sweep on a colder, headless machine reproduced the
sequential baseline within about $3\%$ and the overall shape of the scaling
curves, which supports reproducibility; however, the saturated twelve-thread
peaks varied by tens of percent between separate invocations of the same
configuration, an inter-invocation variance that the intra-run coefficient of
variation does not capture. The single-run maxima at the saturation point should
thus be read as indicative rather than exact.

\subsecao{Future Work}

% review: issue #130, comment 063 --- the future-work list no longer promises
% "run on a desktop/server" as an abstract item, since the Ryzen 9 9950X
% portability run already delivers that evidence; the open directions are the
% ones still genuinely unmeasured (PMU telemetry, medians over the saturated i5
% points, repeated dynamic-granularity sampling, and wider architecture/corpus
% coverage).
Four directions follow from these limitations. The first is to add hardware
performance counters to the benchmarks, measuring cache misses, memory bandwidth,
and pipeline stalls directly, so that the memory bottleneck is confirmed with
direct measurements instead of inferred from execution times. The second,
motivated by the re-run above, is to report the saturated i5 operating points as
medians over several independent invocations rather than as the maximum of a
single sweep, so
that the inter-invocation variance is averaged out rather than amplified. The
third is to settle the dynamic-granularity question---the trade-off between task
size and scheduling overhead---with several repetitions per granularity setting,
ideally over an unevenly loaded corpus, since a single invocation per setting is
dominated by the same operating-regime variance. The fourth is to widen the
evaluation across more architectures and corpora---additional microarchitectures,
larger NUMA topologies, and document collections with different content
statistics---building on the two-platform evidence already gathered to map where
strategies such as dictionary sharding might finally become beneficial.
