Advancements in semiconductor technology have historically driven the growth of computational power. For decades, the number of transistors on a chip doubled roughly every eighteen months, an observation known as \textit{Moore's Law} \cite{Pacheco2011}; rising clock speeds translated these denser circuits into proportional single-core performance gains. However, in the mid-2000s, the hardware industry encountered significant physical barriers, such as excessive power consumption and challenges in heat dissipation, which limited the increase in processor clock frequency.

The response to these technological limitations was a change in processor design: instead of focusing on making a single core faster, the emphasis shifted to integrating multiple processing cores onto a single chip. Thus, multi-core processors emerged as the dominant architecture in modern computers. This transition opened up new possibilities for performance enhancement; however, to take advantage of multi-core processors, programs must be intentionally written or adapted to execute tasks in parallel \cite{Pacheco2011}.

This architectural shift from sequential to parallel execution has a profound impact on high-performance applications. In many scenarios, such as bioinformatics pipelines and network intrusion detection, processing large data volumes efficiently is essential. % review: comment 003 (issue #98) — summarize what Aho-Corasick does before naming it
These applications rely on highly efficient multi-pattern-matching algorithms, and the Aho-Corasick algorithm stands out because it can search for many patterns simultaneously while scanning the input only once, achieving linear-time complexity with respect to the size of the input text. Widely adopted in security tools --- including YARA for malware classification and Snort and Suricata for signature-based network intrusion detection \cite{LeeYang2017FHBM} --- the Aho-Corasick algorithm serves as a backbone for multi-pattern search engines \cite{YARADocs}.

Despite its efficiency, the Aho-Corasick algorithm is intrinsically sequential: its automaton processes input strictly left-to-right, with each state transition depending on the preceding one. As a result, when scanning a single large input on a modern multi-core CPU, the entire computational load is concentrated on one core. This serial dependency becomes a major performance bottleneck when scanning large target data, such as full disk images, packet captures, or genomic sequences. Consequently, the disparity between the algorithm's sequential nature and modern hardware's parallel processing capabilities widens as data volumes grow \cite{AhoCorasick1975}.

\subsecao{Motivation}

The intrinsically sequential nature of Aho-Corasick, combined with the prevalence of multi-core architectures in general-purpose computing, presents a clear opportunity for acceleration through parallel computing. Previous studies report speedups on specialized platforms and in specific application domains \cite{Vajira2018}, \cite{LeeYang2017FHBM}; however, the behavior of a shared-memory, multi-threaded implementation on commodity CPUs in the \textit{memory-bound regime} --- where the automaton size far exceeds the last-level cache --- has received comparatively little attention. % review: comment 004 (issue #99) — point to the systematic review
This observation is supported by the systematic literature review presented in Chapter 3.

% epic-03: workstation is the canonical measurement environment; the thesis is
% framed around shared-memory multi-core CPU parallelism.
As pattern sets for tools such as Snort and Suricata grow in size, the corresponding Aho-Corasick automata can occupy hundreds of megabytes, pushing the hot data structure well beyond the cache hierarchy \cite{Aldwairi2018Characterizing}. In this regime, the primary performance bottleneck shifts from computation to memory bandwidth \cite{Sitaridi2016SIMD}, \cite{LeeYang2017FHBM}. % review: comment 005 (issue #100) — citation for the memory-bandwidth claim
The interaction of multiple threads sharing the same last-level cache changes the scaling behavior in ways that compute-bound models do not capture. Large signature sets such as those of Snort and Suricata are one prominent example of how such automata arise in practice; understanding the limits of parallel scaling on these realistic workloads, measured on a homogeneous multi-core workstation, is the motivation for this study, with intrusion detection serving as a representative application rather than the object of the work.

\subsecao{Objectives}

The general objective of this thesis is to design, implement, and evaluate a parallel version of the Aho-Corasick algorithm targeting shared-memory multi-core CPU architectures, using the POSIX Threads programming model, in order to accelerate multi-pattern matching on large inputs.

To achieve this general objective, the following specific objectives are defined:
\begin{enumerate}
    % review: comment 006 (issue #101) — add the objective of conducting the systematic review
    \item To conduct a systematic literature review of parallelization and optimization techniques for the Aho-Corasick algorithm on multi-core CPUs, in order to identify the state of the art and delimit the research gap addressed by this work;
    \item To design and implement a parallel version of the Aho-Corasick algorithm in C, using the pthreads API, exploiting intra-input parallelism on shared-memory multi-core CPUs;
    \item To conduct a rigorous experimental evaluation on a shared-memory multi-core workstation that quantifies the performance gains of the parallel implementation in terms of speedup, throughput, and parallel efficiency, against a sequential baseline;
    \item To analyze the scalability of the proposed solution under different workload, pattern-set, and thread-count configurations.
\end{enumerate}

\subsecao{Structure of the Thesis}

This document is organized as follows. Chapter 2 presents the Theoretical Framework, introducing the fundamentals of parallel computing, including architectures, performance metrics, and thread-based programming models, with emphasis on the POSIX Threads API. It also discusses the core data structures and algorithms relevant to this work, including Tries, the general pattern-matching problem, and a detailed analysis of the Aho-Corasick algorithm. Chapter 3 describes the Systematic Literature Review, presenting the research questions, search strategy, and selection criteria adopted to identify the state of the art and define the research gap. Chapter 4 presents the Proposed Solution, detailing the parallel-scanning strategy, the boundary-overlap and load-balancing mechanisms, and the flattened output layout that constitute the design. Chapter 5 describes the Methodology, specifying the workstation-based experimental environment, datasets, metrics, measurement protocol, correctness validation, and the hypotheses that the experiments are designed to test. Chapter 6 reports and discusses the Results, isolating the contribution of each optimization, including short diagnostic comparisons of the load imbalance caused by heterogeneous cores and by skewed input content, and positioning the findings against the related literature. Finally, Chapter 7 presents the Conclusion, summarizing the contributions, the threats to validity, and directions for future work.
% Fim do conteúdo da seção de Introdução.
