% review: issue #142, comment 31 --- direct, non-marketing opening
This chapter describes the experimental methodology used to evaluate the
parallel Aho--Corasick scanning strategies introduced in the previous chapter.
The evaluation targets three properties of each strategy --- search
performance, scalability with the number of threads, and correctness with
respect to the sequential baseline --- under a shared-memory multi-core
environment and over pattern dictionaries and text corpora representative of
signature-based intrusion detection. Because the workloads of interest produce
automata whose footprint far exceeds the last-level cache, the reported figures
are expressed as relative quantities (speedup, throughput, and parallel
efficiency) rather than as absolute production capacity, so that the
conclusions concern scaling behaviour instead of the peak rating of a single
machine.

% review: issue #143, comment 32 --- chapter roadmap instead of "principles"
The chapter first establishes the experimental environment and software
stack; then characterizes the pattern dictionaries and text corpora and the
role each one plays; states the three-phase execution model and the invariants
that make the parallelization sound; enumerates the evaluated strategies and
the axes along which they compose; separates the performance metrics from the
supporting diagnostic instrumentation; defines the per-phase measurement
protocol; describes how correctness was established before any performance was
reported; and closes with the experimental design, stating each hypothesis, the
experiment that tests it, and the section of the next chapter that reports the
outcome.

\subsecao{Experimental Environment}

% review: issue #144, comment 33 --- state the single measurement platform directly
% epic-03: workstation (Ryzen 9 9950X, Zen 5) is now the sole canonical platform;
% the heterogeneous processor is reserved for the P/E comparison (task 06).
The measurement platform, and the source of every headline number, table, and
figure in this work, is an AMD Ryzen~9~9950X processor. It is a homogeneous
design of the Zen~5 generation: sixteen identical cores, each with two-way
simultaneous multithreading (SMT), exposes thirty-two logical hardware threads.
Every core reaches the same maximum clock, so the thread pool carries no
performance/efficiency asymmetry. Because the cores are uniform, a uniform text
partition is naturally load-balanced, and the frequency-weighted, topology-aware
weighting introduced in the previous chapter has little to correct on this
machine --- a point revisited in the load-imbalance comparison against a
heterogeneous processor later in this work. The memory hierarchy comprises a
private $48$~KiB L1 data cache and $1$~MiB of L2 per core, and a non-unified
$64$~MiB L3 organized as two $32$~MiB slices, one per core complex (CCD); an
automaton larger than a single $32$~MiB slice therefore cannot remain resident in
the L3 of one complex. Main memory is $123$~GiB of DDR5, and the aggregate memory
bandwidth is the shared resource for which the parallel scans ultimately contend.

The software stack is a purpose-built laboratory written in C11, compiled with
GCC~13.3.0 using \texttt{-O3 -march=native} and an aggressive warning profile,
and linked against the POSIX Threads library \cite{Nichols1996}. Experiments ran
under Linux (kernel~6.17.0, Ubuntu~24.04). To minimize scheduling and
frequency-scaling artifacts, the CPU frequency governor was set to
\texttt{performance}, holding the cores at their sustained all-core clock
throughout the sweep; the topology-aware searchers
(\texttt{pthread\_chunked\_v3} and \texttt{pthread\_chunked\_v3\_flat})
additionally pin each worker thread to a dedicated logical CPU via
\texttt{pthread\_setaffinity\_np}, while the remaining searchers rely on OS
scheduling without explicit binding. The build was additionally validated under
sanitizer instrumentation, namely the Address and Undefined Behavior sanitizers
and the Thread Sanitizer, as discussed in Section~\ref{subsec:correctness}.

% epic-03: hook reserving the heterogeneous processor for the two closing
% diagnostics (P/E imbalance; content skew, pilot i5_2026-07-02).
Two separate diagnostics appear at the end of the results chapter
(Sections~\ref{subsec:heterogeneous} and~\ref{subsec:skew}), solely to isolate
two load-imbalance effects that the canonical setting cannot exhibit: the
imbalance created by heterogeneous cores and the imbalance created by input
content whose matches concentrate in one region. Both run on a secondary
processor that is not a measurement platform for any of the headline figures
reported here.

\subsecao{Pattern Dictionaries and Text Corpora}

The workloads were chosen to sweep the automaton footprint across the cache
hierarchy while keeping the input text realistic for the intrusion-detection
domain. Table~\ref{tab:datasets} summarizes the pattern dictionaries, which were
derived from publicly available Snort and Emerging Threats rule sets, and
Table~\ref{tab:corpora} summarizes the text corpora.

% review: issue #145, comment 34; issue #115, comment 35 --- replace the
% platform-dependent "cache regime" column with a platform-independent role
\begin{table}[htbp]
    \centering
    \caption{Pattern dictionaries, the resulting automaton footprint, and their experimental role.}
    \label{tab:datasets}
    \small
    \begin{tabular}{@{} l r r r p{4.2cm} @{}}
        \toprule
        \textbf{Dictionary} & \textbf{Patterns} & \textbf{States} & \textbf{Footprint} & \textbf{Experimental role} \\
        \midrule
        Snort-100   & 100      & 1{,}939   & 1.93~MiB   & Smallest automaton; lower-bound contrast regime. \\ \addlinespace
        Snort-1k    & $\sim$1{,}000 & 11{,}974 & 11.92~MiB & Intermediate footprint; brackets the throughput cross-over. \\ \addlinespace
        Snort (full) & 4{,}188  & 55{,}479  & 55.23~MiB  & Primary target dictionary (moderate footprint). \\ \addlinespace
        Emerging Threats & 44{,}678 & 508{,}896 & 506.78~MiB & Largest footprint; most aggressive memory stressor. \\
        \bottomrule
    \end{tabular}

    {\footnotesize\raggedright Derived from the Snort and Emerging Threats rule sets.\par}
\end{table}

\begin{table}[htbp]
    \centering
    \caption{Text corpora used as scanning input.}
    \label{tab:corpora}
    \small
    \begin{tabular}{@{} l r p{7.2cm} @{}}
        \toprule
        \textbf{Corpus} & \textbf{Size} & \textbf{Characterization and role} \\
        \midrule
        SimpleWiki & $\sim$1.19~GiB & Natural-language encyclopedic text with low match density; used as the contrast corpus in the cross-corpus experiment, which isolates the effect of the text content. \\ \addlinespace
        Enron      & $\sim$1.32~GiB & Real e-mail messages with medium match density; the canonical benchmark corpus. \\ \addlinespace
        Enron ($8\times$) & $\sim$10.59~GiB & The Enron corpus replicated eightfold; amortizes the build phase and reduces scheduler noise in the scaling curves. \\ \addlinespace
        Skew pair (uniform / clustered) & $2 \times 4.00$~GiB & Synthetic control pair for the content-skew diagnostic: identical bytes and identical total matches, differing only in whether the match-dense blocks are spread evenly or concentrated in the first quarter of the file. \\
        \bottomrule
    \end{tabular}

    {\footnotesize\raggedright The Enron corpus derives from the public Enron Email Dataset; the skew pair is generated from it as described below.\par}
\end{table}

% review: issue #145, comment 34 --- footprints are platform-independent;
% cache interpretation deferred to the results chapter and tied to a platform
The two smaller dictionaries (Snort-100 and Snort-1k) serve as
\textit{contrast regimes} that bracket the point at which the automaton stops
fitting comfortably in cache; the full Snort dictionary and the Emerging Threats
subset are the actual targets of the study, the latter being the most aggressive
stressor, with an automaton far larger than the last-level cache of any platform
used here. The footprints in Table~\ref{tab:datasets} are reported as absolute,
platform-independent sizes; how each footprint relates to a particular cache
level depends on the machine and is therefore interpreted in the next chapter
against the cache hierarchy of the measurement platform --- the $64$~MiB shared
L3, split into two $32$~MiB per-complex slices.

% pilot i5_2026-07-02: skew corpora generated by scripts/make_skewed_corpus.py
% (8 MiB blocks, HOT_FRAC=0.25, byte/match parity validated by the generator).
The skew pair deserves a note on construction, because the validity of the
content-skew diagnostic rests on a strict invariant. Both corpora are assembled
from the same two $8$~MiB building blocks: a \emph{cold} block taken directly
from the Enron corpus, and a \emph{hot} variant of that block in which fragments
of randomly chosen Snort patterns --- between $80\%$ and $100\%$ of a pattern's
length --- are overwritten at random positions until the block reaches a target
match density. Each corpus concatenates $512$ blocks, of which $128$ are hot:
the uniform variant interleaves one hot block into every four, while the
clustered variant places all hot blocks contiguously in the first quarter of the
file. The two files therefore contain the same blocks and differ only in block
order; the generator verifies that their byte counts and total match counts are
identical, so any throughput difference between them is attributable to the
spatial placement of the match-dense work --- precisely the variable the
diagnostic manipulates.

\subsecao{Execution Model and Invariants}

Every execution of the laboratory follows three strictly separated phases; this
separation is the foundation of the lock-free design.

\begin{enumerate}
    \item \textbf{Construction.} The patterns are inserted into a trie, and a
    breadth-first (BFS) traversal computes the goto, failure, and
    dictionary-suffix links, together with the precomputed output structures.
    The resulting automaton is then declared immutable. % review: issue #148, comment 38
    \item \textbf{Search.} Each worker thread reads the shared, read-only
    automaton and its assigned portion of the input text, emitting matches into
    a private, thread-local list. No mutex or atomic operation is used on the
    hot path, because the automaton is never modified during this phase.
    \item \textbf{Merge.} After all workers join, the master thread concatenates
    the thread-local lists in a deterministic order. This phase is always
    sequential and accounts for a negligible fraction of the total time, so it is
    not a target for optimization.
\end{enumerate}

This study respects a set of non-negotiable invariants that make the
parallelization sound. The automaton is strictly read-only during the search;
the hot loop uses neither locks nor atomics; matches remain thread-local until
the join; and the partitioning preserves match ownership without duplication.
For any text-level partitioning, the minimum overlap between adjacent segments
is $L_{\max}-1$ bytes, where $L_{\max}$ is the length of the longest pattern --- as established in the previous chapter, the smallest margin that guarantees that a boundary-straddling pattern is detected by exactly one worker. Match ownership is made disjoint by assigning each
boundary-crossing match to a single segment according to its end position.

\subsecao{Evaluated Strategies}

% review: issue #116, comment 40 --- show which axes are alternatives vs composable
The strategies are organized as a set of orthogonal design axes so that each
performance effect can be attributed to a single cause. Every variant is a
combination of one choice per axis, all selectable at run time within the same
binary and all sharing the same automaton. The axes, and which choices are
mutually exclusive versus composable, are summarized in
Table~\ref{tab:variants}.

\begin{table}[H]
    \centering
    \caption{Evaluated strategies as orthogonal design axes; the work-distribution
    options are alternatives, while the emission and construction axes compose with any of them.}
    \label{tab:variants}
    \small
    \begin{tabular}{@{} l p{9cm} @{}}
        \toprule
        \textbf{Axis} & \textbf{Options (one per run; mutually exclusive within the axis)} \\
        \midrule
        Work distribution & Sequential baseline; static homogeneous chunking; topology-aware weighted chunking; dynamic chunk dispatch (bag of tasks); dictionary sharding by pattern prefix; two-dimensional sharding $\times$ chunking. \\ \addlinespace
        Emission layout & Chained (pointer-chasing) \emph{or} flattened contiguous output table; composes with any work-distribution choice. \\ \addlinespace
        Construction & Sequential build \emph{or} level-synchronous parallel build (BFS); composes with any work-distribution choice. \\
        \bottomrule
    \end{tabular}

\end{table}

Two of the three axes compose freely. The emission layout (chained
pointer-chasing versus a flattened, contiguous output table) and the
construction mode (sequential versus level-synchronous parallel build) can be
paired with any work-distribution choice and with the sequential baseline,
because the parallel build produces an automaton bit-for-bit identical to the
sequential one and the emission layout does not change which matches are
produced. The work-distribution axis, in contrast, is mutually exclusive: a run
partitions the work in exactly one way. The named searchers in the laboratory
are therefore compositions of these axes --- for example, static chunking with
the flat layout, or topology-aware chunking with the flat layout --- which is
precisely what allows one axis to be varied while the others are held fixed.

% review: issue #149, comment 39 --- topology-aware vs dynamic are distinct axes
% review: issue #170, comment 4
The work-distribution options differ in how they assign work to threads.
Static homogeneous chunking is the control case: it divides the text into equal
segments, one per worker, and adds only the boundary overlap required for
correctness. This policy is appropriate when the processor is homogeneous, as in
the canonical Ryzen~9~9950X workstation used for the headline measurements.

Topology-aware chunking and dynamic dispatch are two \textit{distinct} responses
to the imbalance that equal segments can create on processors whose cores are
not equally fast. Topology-aware chunking is a static policy: during
initialization it reads the operating system's per-core frequency metadata,
assigns each worker to a logical CPU, and sizes the worker's segment in
proportion to that CPU's maximum frequency. Faster cores therefore receive
larger segments before the scan begins. On a homogeneous processor these
frequencies are equal, so the policy collapses to static chunking with explicit
thread affinity.

Dynamic dispatch does not use a hardware model. Instead, it splits the text into
many small, uniform tasks and lets idle workers pull tasks from a shared atomic
counter at run time. Faster cores naturally consume more tasks, so imbalance is
corrected reactively rather than by a precomputed segment size. The later
heterogeneous-core comparison uses the Intel Core i5-1235U only as a diagnostic
P/E case for these policies; it is not part of the canonical measurement
platform and supplies none of the headline performance numbers.

The dictionary-parallelism options partition the pattern set instead of the
text: prefix sharding builds $K$ independent sub-automata, and the
two-dimensional composition combines sharding with text chunking to test whether
the two kinds of parallelism add. An exploratory software-prefetch variant of
the chunked searcher also exists in the laboratory as a microarchitectural
probe; it introduces no new axis and is excluded from the controlled grid and
from the reported results.

\subsecao{Metrics and Instrumentation}

% review: issue #117, comment 41 --- separate performance metrics from diagnostics
The performance metrics follow the standard definitions introduced in the
theoretical framework. Search throughput is reported in MB/s (and, where useful,
in Gbps); speedup is the ratio of sequential to parallel search time, as in
Eq.~\ref{eq:speedup}; and parallel efficiency is the speedup normalized by the
thread count, as in Eq.~\ref{eq:efficiency}. Search time is the quantity these
are derived from, and it is always measured separately from construction time,
so that the cost of rebuilding the automaton --- relevant to rule reloading ---
is never conflated with scanning throughput.

A second group of quantities does not measure performance but supports its
interpretation, and is reported as diagnostic instrumentation rather than as a
result. Per-thread timings and the coefficient of variation across repetitions
measure load balance and stability, respectively: the per-thread spread exposes
synchronization waste at the final barrier, while the coefficient of variation
quantifies how noisy a measurement is rather than how fast it is. Match counts
are recorded for every run as a correctness check, not a performance figure (see
Section~\ref{subsec:correctness}). Construction (build) time is recorded for the
parallel-build experiment. Finally, the laboratory writes every run, together
with a snapshot of its environment, to a structured log that is ingested into an
SQLite database, which is the substrate for all aggregation and cross-checking;
the automaton footprint in bytes is retained there too --- not as a headline
figure, but as the causal variable used to explain throughput across regimes.

\subsecao{Measurement Protocol}

% review: issue #118, comment 42 --- explain warm-up once, up front
Each reported data point follows the per-phase repetition protocol summarized in
Table~\ref{tab:protocol}. Every phase begins with a number of \textit{warm-up}
iterations whose times are discarded: the warm-up pays the one-time costs of
page faults and cache population so that the subsequent timed iterations measure
steady-state behaviour. For each timed series both the mean and the best
(minimum) time are kept; the mean is used for the reported throughput, and the
dispersion between iterations is retained as the stability indicator described in
the previous section.

\begin{table}[H]
    \centering
    \caption{Per-phase repetition protocol of the formal sweep, verified against \texttt{sweep.db}.}
    \label{tab:protocol}
    \small
    \begin{tabular}{@{} c l r r @{}}
        \toprule
        \textbf{Phase} & \textbf{Description} & \textbf{Warm-ups} & \textbf{Timed iters} \\
        \midrule
        A & Speedup curves        & 2 & 5 \\
        B & Footprint sweep       & 2 & 5 \\
        C & Cross-corpus          & 2 & 5 \\
        D & Per-thread diagnostic & 1 & 3 \\
        E & Parallel construction & 0 & 1 \\
        G & Task-granularity sweep & 2 & 5 \\
        \bottomrule
    \end{tabular}

    {\footnotesize\raggedright Verified against \texttt{sweep.db}.\par}
\end{table}

% review: issue #118, comment 42 --- one short paragraph per phase
% review: issue #175, comment 9
\begin{itemize}
    \item \textbf{Phase~A --- Speedup curves.} This phase measures the headline
    scaling result. It sweeps thread counts $T \in \{1,2,4,6,\dots,32\}$ over the
    canonical Enron corpus and $T \in \{1,4,8,16,32\}$ over the eight-fold
    replica, up to the thirty-two hardware threads of the platform, running every
    parallel searcher against the two single-thread baselines, with two warm-ups
    and five timed iterations per point.

    \item \textbf{Phase~B --- Footprint sweep.} Holding the corpus fixed at
    Enron, this phase varies the dictionary across the four footprints of
    Table~\ref{tab:datasets} to locate the throughput cross-over, again with two
    warm-ups and five timed iterations.

    \item \textbf{Phase~C --- Cross-corpus comparison.} Holding the dictionary
    fixed at the full Snort set, this phase compares the natural-language
    SimpleWiki corpus against Enron, with two warm-ups and five timed iterations,
    so that any throughput difference is attributable to the corpus rather than
    to the automaton.

    \item \textbf{Phase~D --- Per-thread diagnostic.} At the full thread count,
    this phase records per-thread timings for each parallel searcher --- one
    warm-up and three timed iterations --- to quantify barrier idle time and load
    balance.

    \item \textbf{Phase~E --- Parallel construction.} This phase compares the
    sequential build against the level-synchronous parallel build across the four
    dictionaries; since only the build time is of interest, each build is timed
    once with no warm-up.

    \item \textbf{Phase~G --- Task granularity.} Holding the searcher,
    dictionary, and corpus fixed at the winning configuration
    (\texttt{pthread\_dynamic\_flat}, full Snort, Enron) at the full thread
    count, this phase sweeps the number of text tokens per dispatched task, with
    two warm-ups and five timed iterations, to measure how the atomic-counter
    contention of the bag-of-tasks scheme trades against load balance.
\end{itemize}

% review: issue #119, comment 43; issue #120, comment 44 --- drop thermal as a
% premise; keep a short measurement limitation only
% epic-03: workstation is a stable desktop under the performance governor; the old
% run-to-run/thermal caveat is replaced by the single-run limitation.
The reported figures must be read with one limitation in mind. Each configuration
was measured in a single end-to-end sweep and was not independently replicated, so
the results are single-run per configuration. The within-run
coefficient of variation, retained for every timed series, is small on this
platform --- typically well below one percent on the headline speedup curves and
never above roughly two percent --- which indicates that individual data points
are stable; it does not, however, substitute for between-run replication.
% pilot i5_2026-07-02, phase R: five independent invocations per configuration on
% the secondary processor; tight up to T=8, unstable at that machine's full T=12.
The content-skew diagnostic of the next chapter follows a stricter protocol on
this point: each of its configurations is executed as five independent process
invocations, each with one warm-up and three timed iterations, and the reported
value is the median across invocations. A replication pilot run under the same
protocol on the secondary processor, over the canonical corpus, illustrates why
the distinction matters: up to eight threads the five invocations agree closely,
but at that machine's full logical thread count the between-run dispersion grows
large even though each individual run remains internally stable --- a caution
against reading any single invocation at a saturated operating point as
definitive. Independent replication of the key configurations on the canonical
workstation, reported as a median and interquartile range, is left as a
strengthening of the present single-run figures. The desktop platform runs under
the \texttt{performance} governor at a sustained all-core clock, so the
published values are steady-state rather than short-burst figures.

\subsecao{Correctness Validation}
\label{subsec:correctness}

% review: issue #121, comment 45 --- intro on why correctness matters, then one
% paragraph per validation level
Correctness is a precondition for any performance claim: a faster scan is
worthless if it does not return exactly the matches that the sequential algorithm
returns. The goal of every optimization here is to reduce execution time while
preserving the output of the sequential baseline, so each parallel variant was
required to reproduce that output before it was benchmarked. Correctness was
established at three complementary levels, described in turn below.

First, at the level of the match \emph{set}, the automated test suite requires
every strategy to reproduce the exact set of matches of the sequential baseline
--- each match identified by its end position and pattern identifier --- across
thread counts of $\{1,2,3,4,7,8\}$. The same suite verifies that the
level-synchronous parallel construction yields an automaton bit-for-bit identical
to the sequentially built one, so that swapping in the parallel build can never
alter the reported matches.

Second, at the level of the full-scale \emph{multiset}, the MD5 digest of the
canonicalized match stream --- the complete set of matches placed in a
deterministic order by end position and pattern identifier --- was computed for
each parallel strategy on the production-scale workloads and compared against the
digest of the sequential baseline. Agreement certifies the exact multiset of
matches (their count, end positions, and pattern identifiers), a far stronger
guarantee than match-count parity; it held for every strategy up to a thread
count of $64$, a $2\times$ oversubscription of the thirty-two hardware threads,
demonstrating that the partitioning logic is robust well beyond the physical
thread count.

Third, at the level of segment boundaries and emission order, the strategies
whose thread-local results are merged in text order (the static-chunking
strategies) reproduce even the digest of the raw, un-canonicalized emission
stream, confirming that every boundary-straddling match is assigned to exactly
one segment. The dynamic-dispatch and dictionary-sharded strategies emit the
identical multiset in a different order, so for them only the canonicalized digest
coincides, which is the expected and correct behaviour.

Finally, ThreadSanitizer reported no data races during the parallel search,
empirically confirming the read-only-automaton invariant and the absence of
unsynchronized shared writes on the hot path.

\subsecao{Experimental Design and Hypotheses}

% review: issue #122, comment 46 --- tie hypotheses to the objective and map each
% one to an experiment and to the section of the next chapter that reports it
The objective of this work is to accelerate multi-pattern matching by
parallelizing Aho--Corasick on shared-memory multi-core CPUs. That objective is
decomposed into a set of explicit hypotheses, each phrased so that an experiment
can falsify it and each isolating a single design axis while the others are held
fixed. Table~\ref{tab:hypotheses} maps every hypothesis to the experiment that
tests it and to the place in the next chapter where its outcome is reported;
throughout, the comparison is against the sequential baseline for headline
speedup and against the strongest text-parallel strategy when the question
concerns composition.

% review: issue #177, comment 11
\begin{table}[htbp]
    \centering
    \caption{Hypotheses, the experiment that tests each one, and where the outcome is reported.}
    \label{tab:hypotheses}
    \small
    \begin{tabular}{@{}
        >{\raggedright\arraybackslash}p{5.7cm}
        >{\raggedright\arraybackslash}p{3.2cm}
        >{\raggedright\arraybackslash}p{2.8cm}
    @{}}
        \toprule
        \textbf{Hypothesis} & \textbf{Experiment} & \textbf{Reported in} \\
        \midrule
        Text chunking scales sublinearly on a multi-core CPU but suffers load imbalance when segments are sized uniformly. & Speedup curves (Phase~A) & Fig.~\ref{fig:speedup} \\ \addlinespace
        The automaton footprint, not the corpus content, governs throughput once the working set escapes the cache. & Footprint and cross-corpus sweeps (Phases~B--C) & Table~\ref{tab:footprint} \\ \addlinespace
        The flattened output layout reduces emission cost in both the sequential and the parallel case. & Layout comparison & Table~\ref{tab:flat} \\ \addlinespace
        On homogeneous cores, dynamic dispatch balances the workers at least as well as static chunking, while static frequency weighting adds overhead rather than benefit. & Per-thread diagnostic (Phase~D) & Table~\ref{tab:balance} \\ \addlinespace
        Coarser task granularity improves the dynamic scheduler by amortizing atomic-counter contention. & Task-granularity sweep (Phase~G) & Table~\ref{tab:granularity} \\ \addlinespace
        A level-synchronous parallel construction reduces build time for large dictionaries. & Build sweep (Phase~E) & Table~\ref{tab:build} \\ \addlinespace
        Prefix-based dictionary sharding recovers throughput in the memory-bound regime by shrinking the per-shard working set. & Sharding experiment & Table~\ref{tab:shard} \\ \addlinespace
        A two-dimensional composition of sharding and chunking combines cache locality with text parallelism. & Composition experiment & Table~\ref{tab:twod} \\ \addlinespace
        When matches concentrate in one region of the input, static partitions lose throughput to barrier idle, while dynamic dispatch redistributes the work. & Content-skew diagnostic & Table~\ref{tab:skew} \\
        \bottomrule
    \end{tabular}

\end{table}

Each row answers a different question: how performance scales with threads, what
governs throughput, whether the emission layout pays off, how the workers stay
balanced and how task granularity tunes the dynamic scheduler, whether
construction parallelizes, whether dictionary parallelism helps on its own or
in composition, and whether the dynamic scheduler's balancing advantage
materializes when the input content is skewed. Several hypotheses anticipate
negative or qualified outcomes, and reporting a strategy that fails to outperform
a simpler counterpart is treated as a result in its own right, since it delimits
where plausible optimizations stop paying off on this class of hardware. The next
chapter presents the outcome of this plan, following the same order.
