This chapter presents and discusses the empirical results, following the
protocol described in the previous chapter. All search and construction figures
reported here come from the same sustained measurement campaign; the end-to-end
pipeline times evaluated later in this chapter were collected in a dedicated
benchmark on the same platform and under the same correctness constraints. Every parallel strategy was first verified
to reproduce the exact match set of the sequential baseline. The
analysis proceeds in a deliberate order: it first characterizes the bottleneck
that motivates the entire study (the relationship between automaton footprint
and throughput); it then isolates the contribution of each optimization axis;
and it finally reports the cumulative behaviour at scale, including the
strategies that did not pay off. Throughout, speedup is measured against the
single-threaded sequential baseline, and the reported values are the sustained,
under-load figures, which are conservative relative to cold-burst peaks.

\subsecao{Characterizing the Bottleneck: Footprint versus Throughput}

The defining characteristic of the problem is that throughput is governed by the
size of the automaton, not by the content of the text. Table~\ref{tab:footprint}
sweeps the dictionary from one hundred patterns to roughly forty-five thousand,
keeping the corpus fixed, and reports the single-threaded scanning throughput.
Isolating the effect with a single thread removes any threading confound, so the
degradation can be attributed entirely to the memory hierarchy.

\begin{table}[htbp]
    \centering
    \caption{Single-threaded throughput as the automaton footprint grows.}
    \label{tab:footprint}
    \small
    \begin{tabular}{@{} l r r l r @{}}
        \toprule
        \textbf{Dictionary} & \textbf{Patterns} & \textbf{Automaton} & \textbf{Cache regime} & \textbf{Throughput} \\
         & & & & \textbf{(MB/s)} \\
        \midrule
        Snort-100        & 100      & 1.93~MiB   & Well within L3       & 483.1 \\ \addlinespace
        Snort-1k         & $\sim$1{,}000 & 11.92~MiB & Near L3           & 337.3 \\ \addlinespace
        Snort (full)     & 4{,}188  & 55.23~MiB  & Exceeds L3           & 240.7 \\ \addlinespace
        Emerging Threats & 44{,}678 & 506.78~MiB & $42\times$ the L3    & 125.6 \\
        \bottomrule
    \end{tabular}

    {\footnotesize\raggedright \textbf{Source:} Prepared by the author. Corpus fixed; single thread.\par}
\end{table}

Throughput falls monotonically by $74.0\%$, from $483.1$~MB/s when the automaton
fits comfortably within the shared L3 to $125.6$~MB/s when it is forty-two times
larger than that same cache.
The cause is structural: each input byte triggers a lookup in the
state-transition table, and once that table no longer fits in cache, every
transition risks a main-memory access. The degradation persists in parallel execution: at twelve threads, the speedup of the same topology-aware chunked strategy drops from $6.68\times$ in the
cache-resident regime to $2.63\times$ in the memory-bound regime, confirming
that the limit is the memory subsystem rather than a threading artifact. This is
the central obstacle to scaling Aho-Corasick at intrusion-detection scale, and
it frames the interpretation of every subsequent result.

\subsecao{Scalability of Text Parallelism}

The primary parallelization strategy partitions the input text across worker
threads. Figure~\ref{fig:speedup} shows the speedup as a function of thread
count for the two representative regimes, measured on the largest corpus
($\sim$10.6~GiB) to minimize scheduler and thermal noise.

\begin{figure}[htbp]
\centering
\caption{Speedup of text parallelism versus thread count, for a moderate
dictionary (Snort, 55~MiB; \texttt{pthread\_chunked\_v3\_flat}) and a
memory-bound dictionary (Emerging Threats, 507~MiB;
\texttt{pthread\_chunked\_flat}), on the $\sim$10.6~GiB corpus
(\texttt{enron\_x8}).}
\begin{tikzpicture}
\begin{axis}[
    width=0.82\textwidth,
    height=6.2cm,
    xlabel={Number of threads ($T$)},
    ylabel={Speedup vs.\ sequential},
    xmin=1, xmax=12,
    ymin=1, ymax=5,
    xtick={1,2,4,6,8,10,12},
    ytick={1,2,3,4,5},
    legend pos=north west,
    grid=both,
    grid style={line width=.1pt, draw=gray!10},
    major grid style={line width=.2pt, draw=gray!20},
    style={font=\small}
]
\addplot[color=blue, mark=square, thick] coordinates {
    (1,1.04) (4,2.43) (8,3.61) (12,4.52)
};
\addlegendentry{Snort (55~MiB)}

\addplot[color=red, mark=triangle, thick] coordinates {
    (1,1.14) (4,1.98) (8,2.64) (12,2.79)
};
\addlegendentry{Emerging Threats (507~MiB)}

\addplot[color=gray, dotted] coordinates {
    (1,1) (5,5)
};
\addlegendentry{Ideal (linear)}
\end{axis}
\end{tikzpicture}
\label{fig:speedup}

{\footnotesize\raggedright \textbf{Source:} Prepared by the author.\par}
\end{figure}

Both regimes scale sublinearly. With the moderate dictionary, the best
text-parallel strategy reaches $4.52\times$ at twelve threads
($1{,}087.1$~MB/s; CV~$10\%$); on the canonical corpus, the dynamic-dispatch
strategy peaks slightly higher at $4.79\times$ ($1{,}148.1$~MB/s; CV~$2\%$), the highest
search speedup observed on the intrusion-detection-scale dictionaries. With the memory-bound dictionary, the
curve flattens far earlier: the best strategy reaches only $2.79\times$ at
twelve threads (CV~$8\%$), and on the canonical corpus the peak occurs near six threads
($2.85\times$; CV~$16\%$) and then \textit{regresses} as more threads are added. This early
plateau is the most important observation of the scaling analysis. Once the
automaton is forty-two times larger than the cache, the shared DRAM bus
saturates, and adding more threads (especially the slower Efficiency cores past
the two Performance cores) no longer buys throughput. The physical limit is
memory bandwidth, not the number of cores.

For the moderate-dictionary regime, where memory bandwidth is not the binding constraint, the $4.52\times$ ceiling at twelve threads is consistent with Amdahl's law~\cite{Grama2003}: the observed $37.7\%$ parallel efficiency implies an inherent serial fraction of approximately $15\%$---arising from merge coordination and work dispatch---compounded by the P/E asymmetry of the thread pool, in which the four Performance-core hardware threads carry disproportionately more per-thread weight than the eight Efficiency cores.

Parallel efficiency (Eq.~\ref{eq:efficiency}) quantifies this overhead directly: at
twelve threads, the moderate-dictionary regime achieves $37.7\%$ efficiency ($4.52\times
/ 12$), while the memory-bound regime achieves only $23.3\%$ ($2.79\times / 12$). The
gap between the two is attributable primarily to DRAM saturation rather than to
threading overhead, since it mirrors the cache-residency difference and not the
per-thread synchronization cost.

A separate experiment fixed the dictionary and strategy while changing the
corpus, to confirm that the content of the text is not the governing variable.
The sequential throughput on the two corpora is nearly identical
($241.0$~MB/s versus $248.4$~MB/s), and the twelve-thread speedup differs only
modestly ($4.42\times$ on the e-mail corpus versus $3.66\times$ on the
encyclopedic corpus), a gap within the run-to-run dispersion of the e-mail
measurement (CV $\approx 66\%$). Because Aho-Corasick performs one transition per input
byte regardless of match density, the footprint of the automaton dominates the
behaviour far more than the nature of the corpus.

\subsecao{The Flattened Output Layout}

The proposed output-layout optimization replaces the pointer-chasing emission of
matches with a sequential read of a contiguous array. Because it changes only
the memory layout, its effect can be measured in isolation on a single thread.
Table~\ref{tab:flat} shows that the gain is regime-dependent and, importantly,
grows precisely as memory pressure increases.

\begin{table}[htbp]
    \centering
    \caption{Single-threaded gain of the flattened output layout, by regime.}
    \label{tab:flat}
    \small
    \begin{tabular}{@{} l r r r r @{}}
        \toprule
        \textbf{Regime (dictionary)} & \textbf{Automaton} & \textbf{Baseline} & \textbf{Flattened} & \textbf{Gain} \\
         & & \textbf{(MB/s)} & \textbf{(MB/s)} & \\
        \midrule
        Snort-100 ($\ll$L3)      & 1.93~MiB   & 483.1 & 488.1 & $+1.0\%$ \\ \addlinespace
        Snort (full, $>$L3)      & 55.23~MiB  & 240.7 & 252.0 & $+4.7\%$ \\ \addlinespace
        Emerging Threats ($\gg$L3) & 506.78~MiB & 125.6 & 142.0 & $+13.0\%$ \\
        \bottomrule
    \end{tabular}

    {\footnotesize\raggedright \textbf{Source:} Prepared by the author. Single thread.\par}
\end{table}

When the automaton fits in cache, the optimization is essentially free of
benefit ($+1.0\%$), because the linked structures are already cache-resident.
When the automaton is far larger than the cache, the contiguous layout avoids
the scattered misses of the pointer walk and delivers $+13.0\%$ on a single
thread, which is the cheapest gain available in the memory-bound regime. In the
parallel case, the layout is inherited by the chunked strategies, and the
flattened variants lead or tie their pointer-chasing counterparts in both intrusion-detection-scale regimes; the best results --- $4.52\times$ for the moderate dictionary at the multi-gigabyte scale and $2.85\times$ at the peak of the memory-bound regime on the canonical corpus --- come from strategies that incorporate this layout. It is
worth noting that the gain does not compound multiplicatively with text
parallelism in the moderate regime: there, the DRAM stalls of the transition
table already partially mask the emission cost, so the layout contributes a more
modest increment than its single-threaded figure would suggest. The optimization
is therefore best described as a cheap, broadly applicable improvement whose
payoff is largest exactly where the problem is hardest.

\subsecao{Load Balancing on Heterogeneous Cores}

On the hybrid processor, uniformly sized text segments create stragglers: the
threads assigned to Efficiency cores finish later than those on the faster
Performance cores, and the early finishers idle at the barrier. The effect is
visible not in the mean throughput but in its stability across repetitions.
Table~\ref{tab:balance} reports, for the canonical workload at twelve threads,
the coefficient of variation of the per-iteration timing.

\begin{table}[htbp]
    \centering
    \caption{Run-to-run stability of the text-parallel strategies (twelve threads).}
    \label{tab:balance}
    \small
    \begin{tabular}{@{} l r r @{}}
        \toprule
        \textbf{Strategy} & \textbf{Throughput (MB/s)} & \textbf{Variation (CV)} \\
        \midrule
        Static homogeneous chunking            & 1{,}064.7 & $39.9\%$ \\ \addlinespace
        Static chunking (cache-padded)         & 902.0     & $52.9\%$ \\ \addlinespace
        Topology-aware (frequency-weighted)    & 879.8     & $1.7\%$  \\ \addlinespace
        Dynamic dispatch                       & 864.4     & $3.3\%$  \\ \addlinespace
        Flattened output with chunking         & 1{,}007.2 & $0.4\%$  \\ \addlinespace
        Topology-aware with flattened output   & 994.2     & $4.3\%$  \\
        \bottomrule
    \end{tabular}

    {\footnotesize\raggedright \textbf{Source:} Prepared by the author. Canonical workload, twelve threads; dedicated stability diagnostic (three timed iterations under sustained load). The mean throughputs are subject to the run-to-run variance the table quantifies and are not directly comparable with the sustained figures of the scalability analysis.\par}
\end{table}

The static homogeneous strategies exhibit a coefficient of variation between
$39.9\%$ and $52.9\%$, consistent with stragglers on the slow cores intermittently lengthening the critical path. Both
remedies proposed in the design collapse this dispersion: frequency-weighted
partitioning reduces it to $1.7\%$ and dynamic dispatch to $3.3\%$, while the
flattened chunking strategy is the most stable of all (down to $0.4\%$) --- indicating that uniform partitioning makes the run-to-run timing sensitive to how the scheduler places the slow-core segments, rather than imposing a fixed penalty. The correct
reading is that topology awareness does not make the transition function faster;
it removes synchronization waste at the barrier, trading a marginal change in
mean throughput for a large gain in predictability. This is valuable for
reproducibility and worst-case latency, but it does not by itself change the
ranking of strategies, because the underlying ceiling remains the memory
subsystem.

\subsecao{Parallel Construction of the Automaton}

The construction phase can also be parallelized, because each level of the
breadth-first traversal that computes the failure links depends only on shallower
levels and can therefore be processed in parallel with a barrier between levels.
The trie insertion remains sequential; only the traversal is parallelized.
Table~\ref{tab:build} reports the resulting build speedup.

\begin{table}[htbp]
    \centering
    \caption{Speedup of the parallel automaton construction.}
    \label{tab:build}
    \small
    \begin{tabular}{@{} l r r l @{}}
        \toprule
        \textbf{Dictionary} & \textbf{States} & \textbf{Sequential build} & \textbf{Parallel build} \\
         & & \textbf{(ms)} & \\
        \midrule
        Snort-100        & 1{,}939   & 1.5   & Regresses (overhead dominates) \\ \addlinespace
        Snort (full)     & 55{,}479  & 48.2  & $1.19\times$ peak (four threads) \\ \addlinespace
        Emerging Threats & 508{,}896 & 485.2 & $1.55\times$ peak (eight threads) \\
        \bottomrule
    \end{tabular}

    {\footnotesize\raggedright \textbf{Source:} Prepared by the author.\par}
\end{table}

Parallel construction only pays off for the large dictionary, where it reduces
the build time from $485$ to roughly $313$~milliseconds ($1.55\times$ at eight
threads, falling to $1.41\times$ at twelve). For the small dictionaries the
per-level spawn-and-join overhead exceeds the work, and the build slows down.
This optimization should therefore be understood as an operational benefit, a
reduction in rule-reloading latency for systems that frequently update their
signatures, rather than as a contribution to scanning throughput; on the
multi-gigabyte workloads it accounts for less than $1\%$ of the total time.

\subsecao{Partitioning the Dictionary: A Qualified Negative Result}

Partitioning the dictionary, rather than the text, was evaluated as a contrast,
assigning patterns to shards by their first byte (prefix sharding).
Table~\ref{tab:shard} compares it against plain text parallelism on the
canonical workload.

\begin{table}[htbp]
    \centering
    \caption{Dictionary sharding compared to text parallelism (Snort, canonical corpus).}
    \label{tab:shard}
    \small
    \begin{tabular}{@{} l r r r @{}}
        \toprule
        \textbf{Strategy} & \textbf{Throughput (MB/s)} & \textbf{vs.\ sequential} & \textbf{vs.\ text parallelism} \\
        \midrule
        Dictionary sharding (by prefix)  & 327.2 & $1.37\times$ & $0.34\times$ \\ \addlinespace
        Text chunking with flat output   & 976.1 & $4.07\times$ & $1.00\times$ \\
        \bottomrule
    \end{tabular}

    {\footnotesize\raggedright \textbf{Source:} Prepared by the author. Sharding at its best shard count (six); text chunking at twelve threads.\par}
\end{table}

Prefix sharding reaches $1.37\times$ over the baseline, and its gain saturates
almost immediately --- $1.35\times$ at two shards, within $2\%$ of the six-shard peak, declining thereafter --- which indicates that the benefit comes from
improved cache locality within each smaller sub-automaton rather than from
genuine aggregate parallelism. Even at its best it attains only about a third of
the throughput of plain text parallelism. The conclusion is that, on this class
of hardware, partitioning the text dominates partitioning the dictionary: a real
but small effect, not a competitive strategy.

\subsecao{Composing Sharding with Chunking: A Falsified Hypothesis}

A natural conjecture is that combining dictionary sharding (for cache locality)
with text chunking (for parallelism) would recover the throughput lost in the
memory-bound regime, by making each sub-automaton small enough to approach the
cache. Table~\ref{tab:twod} tests this two-dimensional composition against flat-output
text chunking and falsifies the conjecture.

\begin{table}[htbp]
    \centering
    \caption{Two-dimensional composition versus flat-output text chunking (twelve threads).}
    \label{tab:twod}
    \small
    \begin{tabular}{@{} l r r r @{}}
        \toprule
        \textbf{Workload} & \textbf{Composition} & \textbf{Text chunking} & \textbf{Ratio} \\
         & \textbf{(MB/s)} & \textbf{(MB/s)} & \\
        \midrule
        Snort, canonical corpus              & 785.4 & 976.1 & $0.80\times$ \\ \addlinespace
        Snort, $\sim$10.6~GiB                & 861.6 & 1{,}073.3 & $0.80\times$ \\ \addlinespace
        Emerging Threats, canonical corpus   & 289.0 & 312.3 & $0.93\times$ \\ \addlinespace
        Emerging Threats, $\sim$10.6~GiB     & 314.5 & 350.0 & $0.90\times$ \\
        \bottomrule
    \end{tabular}

    {\footnotesize\raggedright \textbf{Source:} Prepared by the author. Twelve threads in both columns; the comparator is the flat-output text chunking of Table~\ref{tab:shard}.\par}
\end{table}

The composition is slower than flat-output text chunking in every measured scenario,
between $7\%$ and $20\%$. The reason is that each shard must scan the entire
input text, so $K$ shards multiply the text traffic on the memory bus by a factor
of $K$. In the memory-bound regime that traffic is already the bottleneck, so
the extra reads outweigh any locality gained inside the smaller sub-automata. To
shrink the sub-automaton below the last-level cache for the largest dictionary
would require more than forty shards, multiplying the text traffic
proportionally, which is unrecoverable on a memory bus of this bandwidth. This
negative result is a substantive contribution: it closes a plausible region of
the design space and reinforces the conclusion that text parallelism is the
correct axis on memory-bound workloads.

\subsecao{End-to-End Evaluation}

Finally, the complete pipeline, including construction, search, and merge, was
measured as wall-clock time on the $\sim$10.6~GiB corpus.
Table~\ref{tab:e2e} reports the best end-to-end speedup for each dictionary.

\begin{table}[htbp]
    \centering
    \caption{End-to-end wall-clock speedup on the $\sim$10.6~GiB corpus.}
    \label{tab:e2e}
    \small
    \begin{tabular}{@{} l r r r @{}}
        \toprule
        \textbf{Dictionary} & \textbf{Sequential (ms)} & \textbf{Best parallel (ms)} & \textbf{Speedup} \\
        \midrule
        Snort (full)     & 94{,}706  & 21{,}158 & $4.48\times$ \\ \addlinespace
        Emerging Threats & 198{,}906 & 65{,}428 & $3.04\times$ \\
        \bottomrule
    \end{tabular}

    {\footnotesize\raggedright \textbf{Source:} Prepared by the author. Build, search, and merge combined.\par}
\end{table}

For the moderate dictionary, the full parallel stack delivers up to a
$4.48\times$ end-to-end acceleration, reducing the wall-clock time from roughly
ninety-five seconds to twenty-one. For the memory-bound dictionary, the best
end-to-end figure is $3.04\times$, and it is obtained with flat-output text chunking
and a sequential build, because under sustained load the topology-aware variant
regresses sharply and the parallel build contributes less than one percent of the
total time. This asymmetry is consistent with the rest of the study: in the
memory-bound regime, the simplest strategy that respects the bandwidth ceiling is
the most robust.

\subsecao{Discussion and Positioning}

Taken together, the results support a single coherent conclusion. The dominant
obstacle to accelerating Aho-Corasick at intrusion-detection scale is
microarchitectural: when the automaton greatly exceeds the last-level cache,
performance is limited by the memory subsystem, and the most effective response
is to parallelize the text while keeping the per-byte transition cost as low as
possible. No single strategy wins across all regimes; leadership rotates between
dynamic dispatch (moderate dictionary on the canonical corpus) and the flattened
variants, with and without topology awareness, in the remaining scenarios, which
itself reflects that, as the dictionary grows, the binding
constraint shifts from thread scheduling to DRAM bandwidth --- the regime in which a cache-friendly emission path pays the most.

These findings can be positioned against the related literature. Compared with
approaches that restructure the automaton itself to gain cache friendliness,
such as the head--body decomposition of the matcher for multi-core intrusion
detection~\cite{LeeYang2017FHBM}, the present work attains a comparable order of
magnitude of throughput while leaving the classical automaton mathematically
intact, which keeps correctness easy to validate against the sequential
reference. The failure-less variant of the algorithm designed for massively
parallel accelerators~\cite{Vajira2018} is, by contrast, contraindicated on a
multi-core CPU, because its independent per-byte traversals multiply work in a
way that the memory bus cannot absorb; this is consistent with the negative
result observed here for over-partitioning. Single-threaded vectorized engines
that replace the automaton with SIMD literal matching~\cite{Xu2023Harry} operate
on an orthogonal axis, exploiting data parallelism within a thread rather than
across threads, and are therefore complementary to, rather than competitive
with, the inter-thread parallelism studied here. The observation that
layout-level changes to the emission path yield real gains echoes work on
transition-table compression for the same algorithm~\cite{Regeciova2021MYARA}.
Finally, the use of realistic rule sets and large corpora follows the guidance on
representative signature-based intrusion-detection benchmarks~\cite{Aldwairi2018Characterizing},
which is what allows the memory-bound regime, rather than an artificially
cache-friendly one, to be the object of study.
